---
title: "Using the eikonapir package from scratch"
format: 
  html:
    toc: true
    html-math-method: mathjax
vignette: >
  %\VignetteIndexEntry{GME Offers Data Processing}
  %\VignetteEngine{quarto::html}
---

## Overview

This vignette describes a set of tests to validate the functionality of the `get_timeseries()` function and related functions for retrieving market data. We will test:

1. **Basic function call** with valid parameters
2. **Raw JSON output** from `get_timeseries()`
3. **Retrieve Daily Historical Market Data** using `get_rics_d()`
4. **Retrieve Hourly Time Series Data** using `get_rics_h()`
5. **Retrieve Forward Market Data** using `get_rics_f()`

The tests check that the functions return the expected data types and formats, and help ensure that data retrieval works as expected.

## Setup

Before running the tests, you need to configure the **connection to the Reuters API** and ensure you have the correct environment variables and credentials:

```{r}
#| eval: false

library(data.table)
library(eikondata)
library(echarts4r)
library(reactable)

# Set up proxy and API credentials
set_proxy_port(9000L)
PLEASE_INSERT_REUTERS_KEY = Sys.getenv('REUTERS_KEY')
set_app_id(as.character(PLEASE_INSERT_REUTERS_KEY[1]))
```

## Basic Function Call with Valid Parameters
In this test, we check whether the `get_timeseries()` function works with valid parameters, including RIC, fields, start and end dates, and the interval.

```{r}
#| eval: false

result <- get_timeseries(
  rics = "TTFDA",
  fields = c("TIMESTAMP", "CLOSE"),
  start_date = "2024-01-01T00:00:00",
  end_date = "2024-01-10T00:00:00",
  interval = "daily"
)

```

## Raw JSON Output
In this test, we fetch raw JSON output by setting the `raw_output = TRUE` argument. This test verifies that the `get_timeseries()` function can handle and return raw JSON data.
```{r}
#| eval: false

result_json <- get_timeseries(
  rics = "FDBYc1",
  fields = c("TIMESTAMP", "CLOSE"),
  start_date = "2024-01-01T00:00:00",
  end_date = "2024-01-10T00:00:00",
  interval = "daily",
  raw_output = TRUE
)

```

## Retrieve Daily Historical Market Data
In this test, we use the `get_rics_d()` function to fetch daily market data for a given RIC (`TTFDA`) over a specified date range.
```{r}
#| eval: false

daily_data <- get_rics_d(rics = "TTFDA", from_date = "2020-01-01", to_date = "2023-01-01")

```

## Retrieve Hourly Time Series Data
In this test, we use the `get_rics_h()` function to retrieve hourly time series data for a given RIC (`HEEGRAUCH`) over a specified date range.

```{r}
#| eval: false

hourly_data <- get_rics_h(rics = "GMEIT", from_date = "2020-01-01", to_date = "2020-01-03")

```

## Retrieve Forward Market Data
In this test, we use the `get_rics_f()` function to retrieve forward market data for a specified RIC (`FDBMJ5`) over a specified date range.

```{r}
#| eval: false

forward_data <- get_rics_f(rics = "FDBMJ4^2", from_date = "2023-01-01", to_date = "2023-12-31")

```


## Conclusion
This vignette has demonstrated how to test the `get_timeseries()` function and associated functions (`get_rics_d()`, `get_rics_h()`, and `get_rics_f()`) for retrieving market data. These tests help ensure that the functions return data in the expected format and handle edge cases appropriately.


