---
title: "Using the eikonapir package from scratch"
output: html
---

## Overview

This vignette describes a set of tests to validate the functionality of the `get_timeseries()` function and related functions for retrieving market data. We will test:

1. **Basic function call** with valid parameters
2. **Raw JSON output** from `get_timeseries()`
3. **Retrieve Daily Historical Market Data** using `get_rics_d()`
4. **Retrieve Hourly Time Series Data** using `get_rics_h()`
5. **Retrieve Forward Market Data** using `get_rics_f()`

The tests check that the functions return the expected data types and formats, and help ensure that data retrieval works as expected.

## Setup

Before running the tests, you need to configure the **connection to the Reuters API** and ensure you have the correct environment variables and credentials:

```{r}

library(data.table)
library(eikondata)
library(echarts4r)
library(reactable)

# Set up proxy and API credentials
set_proxy_port(9000L)
PLEASE_INSERT_REUTERS_KEY = Sys.getenv('REUTERS_KEY')
set_app_id(as.character(PLEASE_INSERT_REUTERS_KEY[1]))
```

## Basic Function Call with Valid Parameters
In this test, we check whether the `get_timeseries()` function works with valid parameters, including RIC, fields, start and end dates, and the interval.

```{r}
result <- get_timeseries(
  rics = "TTFDA",
  fields = c("TIMESTAMP", "CLOSE"),
  start_date = "2024-01-01T00:00:00",
  end_date = "2024-01-10T00:00:00",
  interval = "daily"
)

reactable(result)

```

## Raw JSON Output
In this test, we fetch raw JSON output by setting the `raw_output = TRUE` argument. This test verifies that the `get_timeseries()` function can handle and return raw JSON data.
```{r}
result_json <- get_timeseries(
  rics = "FDBYc1",
  fields = c("TIMESTAMP", "CLOSE"),
  start_date = "2024-01-01T00:00:00",
  end_date = "2024-01-10T00:00:00",
  interval = "daily",
  raw_output = TRUE
)

print(result_json)

```

## Retrieve Daily Historical Market Data
In this test, we use the `get_rics_d()` function to fetch daily market data for a given RIC (`TTFDA`) over a specified date range.
```{r}
daily_data <- get_rics_d(rics = "TTFDA", from_date = "2020-01-01", to_date = "2023-01-01")
reactable(daily_data)

```


```{r}
daily_data[, date := as.Date(date)] |> 
  e_charts(date) |> 
  e_line(serie = value, name = "Closing Price") |>
  e_title(text = "Daily Market Data - Closing Price") |>
  e_x_axis(name = "Date") |>
  e_y_axis(name = "Closing Price") |>
  e_theme("shine") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom(show = TRUE) |>
  e_legend(show = FALSE) |>
  e_theme('westeros')
```

## Retrieve Hourly Time Series Data
In this test, we use the `get_rics_h()` function to retrieve hourly time series data for a given RIC (`HEEGRAUCH`) over a specified date range.

```{r}
hourly_data <- get_rics_h(rics = "GMEIT", from_date = "2020-01-01", to_date = "2020-01-03")
reactable(hourly_data)

```

```{r}
# Assuming 'hourly_data' is the result from get_rics_h()
hourly_data[, datetime := as.POSIXct(paste(date, hour), format = "%Y-%m-%d %H")] |> 
  e_charts(datetime) |> 
  e_line(serie = value, name = "Closing Price") |>
  e_title(text = "Hourly Market Data - Closing Price") |>
  e_x_axis(name = "Time", axisLabel = list(formatter = "{HH}:{mm}")) |>
  e_y_axis(name = "Closing Price") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom(show = TRUE) |>
  e_theme("shine") |>
  e_legend(show = FALSE) |>
  e_theme('westeros')
```

## Retrieve Forward Market Data
In this test, we use the `get_rics_f()` function to retrieve forward market data for a specified RIC (`FDBMJ5`) over a specified date range.

```{r}
forward_data <- get_rics_f(rics = "FDBMJ4^2", from_date = "2023-01-01", to_date = "2023-12-31")
reactable(forward_data)

```

```{r}
# Assuming 'forward_data' is the result from get_rics_f()
forward_data[, date := as.Date(date)] |> 
  e_charts(date) |>
  e_line(serie = value, name = "Contract Price", lineStyle = list(color = "orange"), symbol = "none") |>
  e_scatter(serie = value, symbolSize = 8, itemStyle = list(color = "orange"))  |>
  e_title(text = "Forward Market Data - Contract Price") |>
  e_x_axis(name = "Date") |>
  e_y_axis(name = "Contract Price") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom(show = TRUE) |>
  e_theme("shine") |>
  e_legend(show = FALSE) |>
  e_theme('westeros')

```

## Conclusion
This vignette has demonstrated how to test the `get_timeseries()` function and associated functions (`get_rics_d()`, `get_rics_h()`, and `get_rics_f()`) for retrieving market data. These tests help ensure that the functions return data in the expected format and handle edge cases appropriately.


